Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-11 WSSSPE1_report/WSSSPE1_summary_report.tex
Refine abstract.

\begin{abstract} \note{Lead: Sou-Cheng T. Choi}
This document discusses the First Workshop on Sustainable Software for Science:
Practice and Experiences (WSSSPE1). The content is based on the workshop
itself, as recorded in a set of collaborative notes taken during the workshop,
including discussion about the keynote presentations, three themed panels that
focused on papers accepted at the workshop, other discussion, cross-cutting
issues, use cases, and conclusions. It joins a nascent literature seeking to
understand what drives software work in science and how the reward systems of
science work, thereby shaping the type of software work undertaken, including the
extent to which developers are motivated to build software for the long-term,
for the use of others, and whether to work collaboratively or separately.
Unique perspectives were captured about issues such as documentation of APIs,
software deployment, and development practices; software licenses; career paths
for developers; identifiers for software through a
mechanism such as a Digital Object Identifier or publication of a ``software
paper''; and evidence of software contribution and impact, recorded in online
systems such as source code repositories like GitHub. For truly sustainable
software, there should be no endpoint, as the software products continue to be
used and useful beyond a single institution, grant, and developer or
development team.

>>>>

\begin{abstract} %\note{Lead: Sou-Cheng T. Choi}
This document summarizes the First Workshop on Sustainable Software for Science:
Practice and Experiences (WSSSPE1). The content is based on the workshop
itself, as recorded in a set of collaborative notes taken during the workshop,
including discussion about the keynote presentations, three themed panels that
discussed papers accepted at the workshop, other discussion, cross-cutting
issues, use cases, and conclusions. It joins a nascent literature seeking to
understand what drives software work in science and how the reward systems of
science work, thereby shaping the type of software work undertaken, including the
extent to which developers are motivated to build software for the long-term,
for the use of others, and whether to work collaboratively or separately.
Unique perspectives were captured about issues such as comprehensive documentation,
software deployment, and development practices; software licenses; career paths
for developers; identifiers for software through a
mechanism such as a Digital Object Identifier or publication of a ``software
paper''; and evidence of software contribution and impact, recorded in online
systems such as source code repositories like GitHub. For truly sustainable
software, there should be no endpoint, as the software products continue to be
used and useful beyond a single institution, grant, and developer or
development team.
